Abstract Binding Trees

### 2015-10-30 paper.tex
Expand on relative monad part

Then, variables object
$\Define{V_s(\Upsilon\parallel\Gamma)}{\MkSet{x\in\Dom\Gamma\mid \Gamma(x)=s}}$
is the unit to this tensor. We will say that an object
$\Of{P}{\widehat{\HypCat}^\Sorts}$ is a $\Sigma$-monoid in case it is equipped
with the following natural transformations:
\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{V}} \arrow[r, "\IMode\nu"]
    \& {\IMode{P}}
    \& {\IMode{P\odot P}}
    \arrow[l, "\IMode\varsigma", swap]
  \end{tikzcd}
\]
Intuitively, $\nu$ embeds variables into $P$ and $\varsigma$ equips $P$ with an
operation for simultaneous substitutions of variables.

\begin{remark}
  A \emph{relative monad} on a functor $\Of{J}{\mathbf{J}\to\mathbf{C}}$ is a
  monoid in the functor category $\mathbf{C}^\mathbf{J}$
  \cite{altenkirch-chapman-uustalu:2015}. A presheaf $P$ with a substitution
  monoidal structure $\Pair{\nu}{\varsigma}$ can be viewed as a relative monad
  on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
\end{remark}

>>>>

Then, variables object
$\Define{V_s(\Upsilon\parallel\Gamma)}{\MkSet{x\in\Dom\Gamma\mid \Gamma(x)=s}}$
is the unit to this tensor. We will say that an object
$\Of{P}{\widehat{\HypCat}^\Sorts}$ is a $\Sigma$-monoid in case it is equipped
with the following natural transformations where $\nu$ embeds variables into $P$
and $\varsigma$ equips $P$ with an operation for simultaneous substitutions of
variables.

\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{V}} \arrow[r, "\IMode\nu"]
    \& {\IMode{P}}
    \& {\IMode{P\odot P}}
    \arrow[l, "\IMode\varsigma", swap]
  \end{tikzcd}
\]

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad} on the functor
  $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.\footnote{Relative monads are
    skew-monoids in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$ \cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} Consequently, the monoid multiplication $\odot$ can be replaced
  with an extension operation:
  \[
    \begin{tikzcd}[ampersand replacement = \&]
      {\IMode{P(\,=\,)^{V(\,-\,)}}} \arrow[r, "(\,-\,)^{P}"]
      \& {\IMode{P(\,=\,)^{P(\,-\,)}}}
    \end{tikzcd}
  \]
\end{remark}
